### 2008-08-19 doc/ws-quick-guide/ws-quick-guide.tex
Rename apinfo -> arcinfo

Now you may use the command line utility ``\texttt{apinfo}'' to obtain a service
description. Make sure user key and certificate and CA certificate(s) are
readable from account you use, and run something like:

\begin{lstlisting}
./apinfo -d VERBOSE -C $HOME/usercert.pem -K $HOME/userkey.pem
 -A /etc/grid-security/certificates https://localhost:60000/arex 2>error.log
\end{lstlisting}

This should produce XML output describing resource A-REX represents.
Listing~\ref{lst:apinfo} shows an example of proper output. In case of error see
\texttt{error.log} file and report problems to ARC development team. Include
content of \texttt{error.log} and server log.

\begin{lstlisting}[caption={Example of a good apinfo output},label=lst:apinfo]
<n:nordugrid xmlns:n="urn:nordugrid" xmlns:M0="urn:Mds"
xmlns:nc0="urn:nordugrid-cluster">
  <nc0:name>mobile2.home.net</nc0:name>
  <nc0:aliasname>MINIMAL Computing Element</nc0:aliasname>
  <nc0:comment>This is a minimal out-of-box CE setup</nc0:comment>
  <nc0:issuerca>/O=Grid/O=Test/CN=CA</nc0:issuerca>
  <nc0:issuerca-hash>4457e417</nc0:issuerca-hash>
  <nc0:trustedca>/O=Grid/O=NorduGrid/CN=NorduGrid Certification
Authority</nc0:trustedca>
  <nc0:trustedca>/O=Grid/O=Test/CN=CA</nc0:trustedca>
  <nc0:contactstring>gsiftp://mobile2.home.net:2811/jobs</nc0:contactstring>
  <nc0:lrms-type>fork</nc0:lrms-type>
  <nc0:architecture>i686</nc0:architecture>
  <nc0:homogeneity>TRUE</nc0:homogeneity>
  <nc0:nodeaccess>inbound</nc0:nodeaccess>
  <nc0:nodeaccess>outbound</nc0:nodeaccess>
  <nc0:totalcpus>1</nc0:totalcpus>
  <nc0:usedcpus>0</nc0:usedcpus>
  <nc0:cpudistribution>1cpu:1</nc0:cpudistribution>
  <nc0:prelrmsqueued>0</nc0:prelrmsqueued>
  <nc0:totaljobs>0</nc0:totaljobs>
  <nc0:sessiondir-free>8469</nc0:sessiondir-free>
  <nc0:sessiondir-total>43865</nc0:sessiondir-total>
  <nc0:sessiondir-lifetime>10080</nc0:sessiondir-lifetime>
  <M0:validfrom>20080220142836Z</M0:validfrom>
  <M0:validto>20080220143036Z</M0:validto>
  <nq0:name xmlns:nq0="urn:nordugrid-queue" name="fork">
    <nq0:name>fork</nq0:name>
    <nq0:status>inactive, grid-manager is down</nq0:status>
    <nq0:comment>This queue is nothing more than a fork host</nq0:comment>
    <nq0:schedulingpolicy>FIFO</nq0:schedulingpolicy>
    <nq0:homogeneity>TRUE</nq0:homogeneity>
    <nq0:nodecpu>Intel(R) Celeron(R) M CPU        420  @ 1.60GHz @ 1596.048
MHz</nq0:nodecpu>
    <nq0:architecture>i686</nq0:architecture>
    <nq0:maxcputime>unlimited</nq0:maxcputime>
    <nq0:maxwalltime>unlimited</nq0:maxwalltime>
    <nq0:running>0</nq0:running>
    <nq0:gridrunning>0</nq0:gridrunning>
    <nq0:localqueued>0</nq0:localqueued>
    <nq0:gridqueued>0</nq0:gridqueued>
    <nq0:prelrmsqueued>0</nq0:prelrmsqueued>
    <nq0:totalcpus>1</nq0:totalcpus>
    <IM0:validfrom>20080220142836Z</M0:validfrom>
    <M0:validto>20080220143036Z</M0:validto>
    <nig0:name xmlns:nig0="urn:nordugrid-info-group" name="jobs">
      <nig0:name>jobs</nig0:name>
      <M0:validfrom>20080220142836Z</M0:validfrom>
      <M0:validto>20080220143036Z</M0:validto>
      <nj0:globalid xmlns:nj0="urn:nordugrid-job"
name="gsiftp://mobile2.home.net:2811/jobs/636312034687631804
289383">

@@

Please note that you can run similar \texttt{apinfo} request against any ARC1
service except Echo service. Output should always be XML description of the service.

>>>>

Now you may use the command line utility ``\texttt{arcinfo}'' to obtain a service
description. Make sure user key and certificate and CA certificate(s) are
readable from account you use, and run something like:

\begin{lstlisting}
./arcinfo -d VERBOSE -C $HOME/usercert.pem -K $HOME/userkey.pem
 -A /etc/grid-security/certificates https://localhost:60000/arex 2>error.log
\end{lstlisting}

This should produce XML output describing resource A-REX represents.
Listing~\ref{lst:arcinfo} shows an example of proper output. In case of error see
\texttt{error.log} file and report problems to ARC development team. Include
content of \texttt{error.log} and server log.

\begin{lstlisting}[caption={Example of a good arcinfo output},label=lst:arcinfo]
<n:nordugrid xmlns:n="urn:nordugrid" xmlns:M0="urn:Mds"
xmlns:nc0="urn:nordugrid-cluster">
  <nc0:name>mobile2.home.net</nc0:name>
  <nc0:aliasname>MINIMAL Computing Element</nc0:aliasname>
  <nc0:comment>This is a minimal out-of-box CE setup</nc0:comment>
  <nc0:issuerca>/O=Grid/O=Test/CN=CA</nc0:issuerca>
  <nc0:issuerca-hash>4457e417</nc0:issuerca-hash>
  <nc0:trustedca>/O=Grid/O=NorduGrid/CN=NorduGrid Certification
Authority</nc0:trustedca>
  <nc0:trustedca>/O=Grid/O=Test/CN=CA</nc0:trustedca>
  <nc0:contactstring>gsiftp://mobile2.home.net:2811/jobs</nc0:contactstring>
  <nc0:lrms-type>fork</nc0:lrms-type>
  <nc0:architecture>i686</nc0:architecture>
  <nc0:homogeneity>TRUE</nc0:homogeneity>
  <nc0:nodeaccess>inbound</nc0:nodeaccess>
  <nc0:nodeaccess>outbound</nc0:nodeaccess>
  <nc0:totalcpus>1</nc0:totalcpus>
  <nc0:usedcpus>0</nc0:usedcpus>
  <nc0:cpudistribution>1cpu:1</nc0:cpudistribution>
  <nc0:prelrmsqueued>0</nc0:prelrmsqueued>
  <nc0:totaljobs>0</nc0:totaljobs>
  <nc0:sessiondir-free>8469</nc0:sessiondir-free>
  <nc0:sessiondir-total>43865</nc0:sessiondir-total>
  <nc0:sessiondir-lifetime>10080</nc0:sessiondir-lifetime>
  <M0:validfrom>20080220142836Z</M0:validfrom>
  <M0:validto>20080220143036Z</M0:validto>
  <nq0:name xmlns:nq0="urn:nordugrid-queue" name="fork">
    <nq0:name>fork</nq0:name>
    <nq0:status>inactive, grid-manager is down</nq0:status>
    <nq0:comment>This queue is nothing more than a fork host</nq0:comment>
    <nq0:schedulingpolicy>FIFO</nq0:schedulingpolicy>
    <nq0:homogeneity>TRUE</nq0:homogeneity>
    <nq0:nodecpu>Intel(R) Celeron(R) M CPU        420  @ 1.60GHz @ 1596.048
MHz</nq0:nodecpu>
    <nq0:architecture>i686</nq0:architecture>
    <nq0:maxcputime>unlimited</nq0:maxcputime>
    <nq0:maxwalltime>unlimited</nq0:maxwalltime>
    <nq0:running>0</nq0:running>
    <nq0:gridrunning>0</nq0:gridrunning>
    <nq0:localqueued>0</nq0:localqueued>
    <nq0:gridqueued>0</nq0:gridqueued>
    <nq0:prelrmsqueued>0</nq0:prelrmsqueued>
    <nq0:totalcpus>1</nq0:totalcpus>
    <IM0:validfrom>20080220142836Z</M0:validfrom>
    <M0:validto>20080220143036Z</M0:validto>
    <nig0:name xmlns:nig0="urn:nordugrid-info-group" name="jobs">
      <nig0:name>jobs</nig0:name>
      <M0:validfrom>20080220142836Z</M0:validfrom>
      <M0:validto>20080220143036Z</M0:validto>
      <nj0:globalid xmlns:nj0="urn:nordugrid-job"
name="gsiftp://mobile2.home.net:2811/jobs/636312034687631804
289383">

@@

Please note that you can run similar \texttt{arcinfo} request against any ARC1
service except Echo service. Output should always be XML description of the service.
